Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-02 paper/paper.tex
added new pipe package

This set of keywords clearly allows a large number of false positives:\\
nice fish and chip.. good pie apple :-) http://t.co/KVDN5r5l \\
20 chicken nuggets, chips, big mac, and a vanilla milkshake LIFE IS GOOD \\
1 more day whoop plus safari ride yay \\
Ashley staples an apple.  "AHHHH!!!!  Apple juice in my eye!" \\
I ain't seen uncle Mac in a while\\

We define a tweet to be "about" Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers. We make the assumption that spam will be filtered from the testing set. This could be done via an existing Naive Bayes classifier, but we simply did not include instances of spam in our corpus during the manual labeling process. We collected our tweets over the course of twelve hours. On Twitter, a single message posted is often reposted, or "re-tweeted," many more times in a very short timespan. Because of the small timespan of our data collection, a large number of retweets (effectively duplicates) appeared in the dataset. We filtered these duplicates out of the dataset as well to prevent over-fitting in our model. After filtering, our original set of 115,000 tweets was reduced to 65,000. A representative sample of non-spam, non-duplicate tweets has composition of 60\% topical instances and 40\% false positives [need to analyze this for sure].
A computer-posted spam tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
A retweet, signified by "RT": RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\

@@

\subsubsection{Feature-space Enrichment}
Stopword removal: In order to improve accuracy of classification we decided to run each tweet through a pipe that would remove stopwords. Stopwords are generally known as adverbs, conjunctions, pronouns, and prepositions commonly found in English sentences, By removing these words, we hoped that the classifiers would be able to focus more on the relevant text and less on meaningless parts of the tweets. Since this is a common task for natural language processing we were able to make use of one of Mallet's stopwords pipes, using a default list of stopwords.
N-grams:
Fix emoticons:
HTML corrections: 
URL replacement:
Spell checking: Since twitter is an informal form of communication, we found that a fair number of tweets were being classified that had misspelled words. We decided that performing a spell check on the tweet might help the classifier work, since then it would only have to process proper English. In order to perform the spell check, we made use of an api that would return suggestions for misspelled words. Along with the suggested correct spellings of words, we were also given a "confidence" level for each suggestion. By using this value we were able to choose the best suggestion, and also filter out any suggestions that were too far from the original word.

\subsubsection{Disambiguation}
Lowercasing:
Stemming: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem. Therefore the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not a real word. We believed that by reducing each word in the tweet to a its stem, we would be able to improve the classifying algorithm's ability to classify. In order to add stemming we made use of an api that used a Porter stemming algorithm to find the stem of each word.

\subsubsection{Tokenization}
Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenization system due to the high level of noise in the feature set [citation and more details]. Tweets are limited to 140 characters, which limits the total number of features possible. Some of the many natural language processing dilemmas present in tweets include excessive and irregular punctuation, frequent misspellings, emoticons, URLs, and hashtags, to name a few.

Cool ranch , 4 berry sundae , apple juice \#yessuh \#latenight \#snack http://t.co/ttc3vujp 
I just poured apple juice on my cereal.. Gah. \#SoTired 
I hate Siri.. -\_\_\_-

@@

Searching for emoticons in this tweet will extract :/ as an emoticon, effectively breaking up the URL.

Now on my iphone ?? http://t.co/Rqr1RL2R

@@

I listen to my iPod every day and it's just broke omg:(!!

@@

After tokenizing these special features in order (URLs, emoticons, usernames, and hashtags) we are left with a fragmented tweet containing myriad punctuation, capitalization, and creative spellings. As done by Potts (2011) we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set. In the following tweet, "loooool" is normalized to "loool".

\#news can't wait for my signed \#OoRITE2OutNow it's emotional here right now loooool \#OoRITE2OutNow https://t.co/r4n4cn6C

>>>>

This set of keywords clearly allows a large number of false positives:\\
\begin{quote}
nice fish and chip.. good pie apple :-) http://t.co/KVDN5r5l \\
20 chicken nuggets, chips, big mac, and a vanilla milkshake LIFE IS GOOD \\
1 more day whoop plus safari ride yay \\
Ashley staples an apple.  "AHHHH!!!!  Apple juice in my eye!" \\
I ain't seen uncle Mac in a while \\
\end{quote}

We define a tweet to be "about" Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers. We make the assumption that spam will be filtered from the testing set. This could be done via an existing Naive Bayes classifier, but we simply did not include instances of spam in our corpus during the manual labeling process. We collected our tweets over the course of twelve hours. On Twitter, a single message posted is often reposted, or "re-tweeted," many more times in a very short timespan. Because of the small timespan of our data collection, a large number of retweets (effectively duplicates) appeared in the dataset. We filtered these duplicates out of the dataset as well to prevent over-fitting in our model. After filtering, our original set of 115,000 tweets was reduced to 65,000. A representative sample of non-spam, non-duplicate tweets has composition of 60\% topical instances and 40\% false positives [need to analyze this for sure].
\begin{quote}
A computer-posted spam tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
A retweet, signified by "RT": RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
\end{quote}

@@

\subsubsection{Feature-space Enrichment}
~\\
\textit{Stopword removal}: In order to improve accuracy of classification we decided to run each tweet through a pipe that would remove stopwords. Stopwords are generally known as adverbs, conjunctions, pronouns, and prepositions commonly found in English sentences, By removing these words, we hoped that the classifiers would be able to focus more on the relevant text and less on meaningless parts of the tweets. Since this is a common task for natural language processing we were able to make use of one of Mallet's stopwords pipes, using a default list of stopwords.\\
\textit{N-grams}:\\
\textit{Fix emoticons}:\\
\textit{HTML corrections}:\\ 
\textit{URL replacement}:\\
Spell checking: Since Twitter is an informal form of communication, we found that a fair number of tweets were being classified that had misspelled words. We decided that performing a spell check on the tweet might help the classifier work, since then it would only have to process proper English. In order to perform the spell check, we made use of an api that would return suggestions for misspelled words. Along with the suggested correct spellings of words, we were also given a "confidence" level for each suggestion. By using this value we were able to choose the best suggestion, and also filter out any suggestions that were too far from the original word.\\

\subsubsection{Disambiguation}
~\\
\textit{Lowercasing}:\\
Stemming: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem. Therefore the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not a real word. We believed that by reducing each word in the tweet to a its stem, we would be able to improve the classifying algorithm's ability to classify. In order to add stemming we made use of an api that used a Porter stemming algorithm to find the stem of each word.\\

\subsubsection{Tokenization}
~\\
Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenization system due to the high level of noise in the feature set [citation and more details]. Tweets are limited to 140 characters, which limits the total number of features possible. Some of the many natural language processing dilemmas present in tweets include excessive and irregular punctuation, frequent misspellings, emoticons, URLs, and hashtags, to name a few.\\

\begin{quote}
Cool ranch , 4 berry sundae , apple juice \#yessuh \#latenight \#snack http://t.co/ttc3vujp 
I just poured apple juice on my cereal.. Gah. \#SoTired 
I hate Siri.. -\_\_\_- 
\end{quote}

@@

Searching for emoticons in this tweet will extract :/ as an emoticon, effectively breaking up the URL.
\begin{quote}
Now on my iphone ?? http://t.co/Rqr1RL2R 
\end{quote}

@@

\begin{quote}
I listen to my iPod every day and it's just broke omg:(!!
\end{quote}

@@

After tokenizing these special features in order (URLs, emoticons, usernames, and hashtags) we are left with a fragmented tweet containing myriad punctuation, capitalization, and creative spellings. As done by Potts (2011) we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set. In the following tweet, "loooool" is normalized to "loool".
\begin{quote}
\#news can't wait for my signed \#OoRITE2OutNow it's emotional here right now loooool \#OoRITE2OutNow https://t.co/r4n4cn6C 
\end{quote}
